\textbf{Are regime changes always bad economics? Evidence from daily financial data}

### 2021-12-13 doc/regime_changes_note_anonymous.tex
Reduced appendix to under 10 pages in manuscript

\begin{table}[H]
\caption{List of stock indices} \label{tab:stock-list}
\vspace{-5pt}
\footnotesize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}lll}
  \hline
  \hline
  \multicolumn{1}{c}{Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Begin Date} &\multicolumn{1}{c}{Start Date}\\
  \hline
Argentina & Beunos Aires SE General Index & Dec-66 & Jan-17\\
Australia & Australia ASX All Ordinaries & Jan-58 & Jan-17\\
Bangladesh & Dhaka SE Index & Jan-90 & Jan-17\\
Canada & Canada S\&P/TSX 300 Composite & Jan-76 & Jan-17\\
Chile & Santiago IGBC General Index & Jan-75 & Jan-17\\
Colombia & Colombia IGBC General Index & Jan-92 & Jan-17\\
Ecuador & Ecuador Bolsa de Valores de Guayaquil (BVG) & Jan-94 & Jan-17\\
Egypt & Cairo SE Index & Dec-92 & Jan-17\\
Emerging Market & S\&P/IFC Emerging Markets Investable Composite & Jul-95 & Jan-17\\
Greece & Athens SE General Index & Oct-88 & Jan-17\\
India & Bombday SE SENSEX & Apr-79 & Jan-17\\
Indonesia & Jakarta SE Composite Index & Apr-83 & Jan-17\\
Iran & Tehran SE Price Index & Jan-95 & Jan-17\\
Israel & Tel Aviv 100 Index & May-87 & Jan-17\\
Japan & Tokyo SE Price Index (TOPIX) & Jan-53 & Jan-17\\
Latin America & Dow Jones Latin America Index & Jan-92 & Jan-17\\
Lithuania & Lithuania Lit-10 Index & Jan-99 & May-05\\
Malaysia & Malaysia KLSE Composite & Jan-80 & Jan-17\\
Nepal & Nepal NEPSE Stock Index & Jan-01 & Jan-17\\
Netherlands & Netherlands All-Share Price Index & Jan-80 & Jan-17\\
Pakistan & Karachi SE 100 Index & Jan-89 & Jan-17\\
Paraguay & Asuncion SE PDV General Index & Oct-93 & Sep-08\\
Peru & Lima SE General Index & Jan-82 & Jan-17\\
Philippines & Manila SE Composite Index & Jan-86 & Jan-17\\
Portugal & Oporto PSI-20 Index & Jan-86 & Jan-17\\
Singapore & Singapore FTSE ST Index & Jul-65 & Jan-17\\
South Korea & Korea SE Stock Price Index  & Jan-62 & Jan-17\\
Southeast Asia & Dow Jones Southeast Asia Index & Jan-92 & Jan-17\\
Spain & Madrid SE General Index & Aug-71 & Jan-17\\
Sri Lanka & Colombo SE All-Share Index & Dec-84 & Jan-17\\
Sweden & Sweden OMX Affarsvarlden General Index & Jan-80 & Jan-17\\
Taiwan & Taiwan SE Capitalization Weighted Index & Jan-67 & Jan-17\\
Thailand & Thailand SET General Index & Apr-75 & Jan-17\\
Tunisia & Tunisia SE Index & Dec-97 & Jan-17\\
Turkey & Instanbul IMKB 100 Price Index & Oct-87 & Jan-17\\
Ukraine & Ukraine PFTS OTC Index & Jan-98 & Jan-17\\
United Kingdom & UK FTSE All-Share Index & Nov-62 & Jan-17\\
United States & Dow Jones Industrial Average & Feb-1885 & Jan-17\\
Uruguay & Bolsa de Valores de Montevideo Index & Jan-08 & Jul-16\\
Venezuela & Dow Jones Venezuela Stock Index & Jan-92 & Jul-07\\
Venezuela & Caracas SE General Index & Jan-94 & Jan-17\\
World & MSCI World Price Index & Jan-76 & Jan-17\\
Zambia & Lusaka SE Index & Jan-02 & Apr-06\\
Zambia & Lusaka SE Index & Jul-11 & Jan-17\\
   \hline
   \hline
\end{tabular*}
\end{threeparttable}
\end{center}
\end{table}

\begin{table}[H]
\caption{Regime changes} \label{tab:regime-changes}
\vspace{-5pt}
\footnotesize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ll}
  \hline
  \hline
  \multicolumn{1}{c}{Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Political Outcome}\\
  \hline
   \multicolumn{3}{c}{\textbf{Coups}}\\ 
\ExpandableInput{../tables/coups.txt} \\
   \multicolumn{3}{c}{\textbf{Failed coup}}\\ 
\ExpandableInput{../tables/failed_coup.txt}\\
  \multicolumn{3}{c}{\textbf{Assassinations}}\\ 
\ExpandableInput{../tables/assassinations.txt}\\
  \multicolumn{3}{c}{\textbf{Resignations}}\\ 
\ExpandableInput{../tables/resignations.txt}
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes: The Polity score is used to classify political outcomes as follows: autocracy = $-10 \leq \rm{score} \leq -6$, anocracy = $-5 \leq \rm{score} \leq 5$, and democracy = $6 \leq \rm{score} \leq 10$.
\end{threeparttable}
\end{center}
\end{table}

\begin{figure}[!ht]
\begin{centering}
\includegraphics[width = 15cm]{../figs/daily_mean_absreturn.pdf}
\caption{Absolute value of daily returns}
\label{fig:AV-DR}
\end{centering}
\end{figure}

\clearpage
\newpage

@@

\newpage

\begin{figure}[!htb]
\includegraphics[scale = 0.75]{../figs/mean-volatility.pdf}
\caption{Mean of volatility estimates from GARCH(1,1) models}
\label{fig:volatility}
\end{figure}

\newpage

\subsection{Event-level estimates: coups} \label{subsec: coups appendix}

@@

\begin{table}[H]
\caption{Abnormal returns following coups} \label{tab:AR-coups}
\vspace{-5pt}
\footnotesize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
  \hline
  \hline
\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
\cmidrule(r){3-5} \cmidrule(r){6-7}
\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
  \hline
\ExpandableInput{../tables/artable-coups-car.txt}
  \hline
\ExpandableInput{../tables/artable-coups-car-mean.txt}
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes: Standard errors are in parentheses. ``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative). Returns are inflation adjusted. 
\end{threeparttable}
\end{center}
\end{table}

\subsection{Event-level estimates: assassinations} \label{subsec: ass appendix}

\begin{table}[H]
\caption{Abnormal returns following assassinations} \label{tab:AR-ass}
\vspace{-5pt}
\footnotesize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
  \hline
  \hline
\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
\cmidrule(r){3-5} \cmidrule(r){6-7}
\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
  \hline
\ExpandableInput{../tables/artable-ass-car.txt}
  \hline
\ExpandableInput{../tables/artable-ass-car-mean.txt}
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes: Standard errors are in parentheses. ``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative). Returns are inflation adjusted. 
\end{threeparttable}
\end{center}
\end{table}

\subsection{Event-level estimates: resignations} \label{subsec: resignation appendix}

\begin{table}[H]
\caption{Abnormal returns following resignations} \label{tab:AR-resignations}
\vspace{-5pt}
\footnotesize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
  \hline
  \hline
\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
\cmidrule(r){3-5} \cmidrule(r){6-7}
\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
  \hline
\ExpandableInput{../tables/artable-res-car.txt}
  \hline
\ExpandableInput{../tables/artable-res-car-mean.txt}
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes: Standard errors are in parentheses. ``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative). Returns are inflation adjusted. 
\end{threeparttable}
\end{center}
\end{table}

\newpage

@@

The resignations studied in this paper are those in which leaders left office because of poor performance, public discontent and popular protests. It is therefore not unreasonable to expect the political actions preceding the resignations to have similarly large effects on financial markets.\footnote{Indeed, corporate investors in the 2013 MIGA \textit{World Investment and Political Risk} ranked civil disturbances as the fourth most concerning type of political risk.} To examine this, we explore all resignations that were driven by significant popular demonstrations, riots, non-violent civil resistance and other forms of public discontent (see \autoref{tab:protest-list}).\footnote{The set of resignations includes all those listed in either the Coup d'etat Events Handbook or the Archigos Version 4.1 data set with available financial data. In practice, this is the 2011 Egyptian Revolution and the list of resignations in \autoref{tab:AR-resignations}.}

\begin{table}[H]
\caption{List of public protests preceding resignations} \label{tab:protest-list}
\vspace{-5pt}
\footnotesize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}llll}
  \hline
    \hline
\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Name}&\multicolumn{1}{c}{Start Date}&\multicolumn{1}{c}{End Date}\\
  \hline
Philippines & EDSA 1/Yellow Revolution & 2/22/1986 & 2/25/1986\\
Bangladesh & Bangladeshi Spring of 1990 & 11/27/1990 & 12/7/1990\\
Thailand & Black May & 5/17/1992 & 5/20/1992\\
Indonesia & Indonesian Riots & 5/12/1998 & 5/21/1998\\
Philippines & EDSA II & 1/17/2001 & 1/20/2001\\
Argentina & Argentina Riots & 12/16/2001 & 12/20/2001\\
Ukraine & Orange Revolution & 11/22/2004 & 1/23/2005\\
Ecuador & Ecuadorian Protests & 4/13/2005 & 4/20/2005\\
Nepal & Nepalese People's Revolution & 4/6/2006 & 4/24/2006\\
Tunisia & Tunisian Revolution & 12/18/2010 & 1/14/2011\\
Egypt & Egyptian Revolution & 1/25/2011 & 2/11/2001\\
   \hline
   \hline
\end{tabular*}
\scriptsize
\end{threeparttable}
\end{center}
\end{table}

A recent example of a popular uprising preceding a resignation is the 2011 Egyptian Revolution that resulted in the overthrow of President Hosni Mubarak's regime.\footnote{Abnormal returns for this event are not shown in \autoref{tab:AR-resignations} because the stock market was closed on the day of Mubarak's resignation.} Clashes between security forces and protestors led to the deaths of hundreds of citizens and injuries to thousands more. The uprising began on January 25, 2011 when millions of protestors demanded the overthrow of the Egyptian leadership. Examples of public discontent included demonstrations, marches, riots, non-violent civil disobedience, and labor strikes.

The short-term impact of the Egyptian Revolution on the economy was disastrous. As shown in \autoref{fig:CAR-Egypt}, abnormal returns on the Egyptian Stock Exchange Index (EGX 30) were around -7\% on January 26th and -10\% the day after. To prevent further decline during the uprising, the Egyptian Stock Exchange closed at the end of trading on January 27th. President Mubarak resigned on February 11, but the market remained closed until March 23, when CARs declined by another 9\%, before rebounding slightly thereafter.

\begin{figure}[!ht]
\includegraphics{../figs/egypt-revolution-2011.pdf}
\caption{Cumulative abnormal returns during the Egyptian revolution}
\label{fig:CAR-Egypt}
\end{figure}

An important question is whether other popular uprisings have had similar adverse economic consequences. To examine this, we explore all resignations that were driven by significant public protests.\footnote{The set of resignations includes all those listed in either the Coup d'etat Events Handbook or the Archigos Version 4.1 data set with available financial data. In practice, this is the 2011 Egyptian Revolution and the list or resignations in \autoref{tab:AR-resignations}.} Public protests include popular demonstrations, riots, non-violent civil resistance and other forms of public discontent. We find that both volatility and the absolute value of returns increase during times of protest. Similarly to coups, however, the direction of returns is dependent upon the nature of the protest in question.

@@

Column (1) suggests that public protests have no effect on stock returns. However, this occurs because some political movements increase stock prices while others decrease them. As shown in column (2), the absolute value of stock returns are approximately 1.5\% higher during public protests. These estimates would be biased if protest dates are correlated with higher world or regional stock market indices. To address this potential confounder, column (3) controls for returns on the S\&P/IFC Emerging Markets Investable Composite Stock Index. The coefficient on \textit{Protest} barely changes and the absolute value of returns are still about 1.5\% higher during public protests. Finally, column (4) shows that stock volatility is approximately 1 percentage point higher during political movements.\footnote{Volatility estimation methodology is described in detail in \nameref{subsec: Volatility}.}

@@

\begin{table}[!ht]
\caption{Effect of public protests on stock prices} \label{tab:protest-stocks}
\vspace{-5pt}
\footnotesize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}d{1.3}d{1.3}d{1.3}d{1.3}}
  \hline
  \hline
\multicolumn{1}{c}{}&\multicolumn{1}{c}{Returns} & \multicolumn{2}{c}{Absolute Value of Returns}&\multicolumn{1}{c}{Volatility}\\
\cmidrule(r){2-2} \cmidrule(r){3-4} \cmidrule(r){5-5}
 & \multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}\\
  \hline
\ExpandableInput{../tables/protest-regtable.txt}
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes: Standard errors clustered by event are in parentheses.
\end{threeparttable}
\end{center}
\end{table}

\clearpage
\pagebreak
\newpage

\subsection{Event-level estimates: democratic vs. authoritarian regime changes}

>>>>

\begin{table}[H]
\caption{List of stock indices} \label{tab:stock-list}
\vspace{-5pt}
\scriptsize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}lll}
  \hline
  \hline
  \multicolumn{1}{c}{Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Begin Date} &\multicolumn{1}{c}{Start Date}\\
  \hline
Argentina & Beunos Aires SE General Index & Dec-66 & Jan-17\\
Australia & Australia ASX All Ordinaries & Jan-58 & Jan-17\\
Bangladesh & Dhaka SE Index & Jan-90 & Jan-17\\
Canada & Canada S\&P/TSX 300 Composite & Jan-76 & Jan-17\\
Chile & Santiago IGBC General Index & Jan-75 & Jan-17\\
Colombia & Colombia IGBC General Index & Jan-92 & Jan-17\\
Ecuador & Ecuador Bolsa de Valores de Guayaquil (BVG) & Jan-94 & Jan-17\\
Egypt & Cairo SE Index & Dec-92 & Jan-17\\
Emerging Market & S\&P/IFC Emerging Markets Investable Composite & Jul-95 & Jan-17\\
Greece & Athens SE General Index & Oct-88 & Jan-17\\
India & Bombday SE SENSEX & Apr-79 & Jan-17\\
Indonesia & Jakarta SE Composite Index & Apr-83 & Jan-17\\
Iran & Tehran SE Price Index & Jan-95 & Jan-17\\
Israel & Tel Aviv 100 Index & May-87 & Jan-17\\
Japan & Tokyo SE Price Index (TOPIX) & Jan-53 & Jan-17\\
Latin America & Dow Jones Latin America Index & Jan-92 & Jan-17\\
Lithuania & Lithuania Lit-10 Index & Jan-99 & May-05\\
Malaysia & Malaysia KLSE Composite & Jan-80 & Jan-17\\
Nepal & Nepal NEPSE Stock Index & Jan-01 & Jan-17\\
Netherlands & Netherlands All-Share Price Index & Jan-80 & Jan-17\\
Pakistan & Karachi SE 100 Index & Jan-89 & Jan-17\\
Paraguay & Asuncion SE PDV General Index & Oct-93 & Sep-08\\
Peru & Lima SE General Index & Jan-82 & Jan-17\\
Philippines & Manila SE Composite Index & Jan-86 & Jan-17\\
Portugal & Oporto PSI-20 Index & Jan-86 & Jan-17\\
Singapore & Singapore FTSE ST Index & Jul-65 & Jan-17\\
South Korea & Korea SE Stock Price Index  & Jan-62 & Jan-17\\
Southeast Asia & Dow Jones Southeast Asia Index & Jan-92 & Jan-17\\
Spain & Madrid SE General Index & Aug-71 & Jan-17\\
Sri Lanka & Colombo SE All-Share Index & Dec-84 & Jan-17\\
Sweden & Sweden OMX Affarsvarlden General Index & Jan-80 & Jan-17\\
Taiwan & Taiwan SE Capitalization Weighted Index & Jan-67 & Jan-17\\
Thailand & Thailand SET General Index & Apr-75 & Jan-17\\
Tunisia & Tunisia SE Index & Dec-97 & Jan-17\\
Turkey & Instanbul IMKB 100 Price Index & Oct-87 & Jan-17\\
Ukraine & Ukraine PFTS OTC Index & Jan-98 & Jan-17\\
United Kingdom & UK FTSE All-Share Index & Nov-62 & Jan-17\\
United States & Dow Jones Industrial Average & Feb-1885 & Jan-17\\
Uruguay & Bolsa de Valores de Montevideo Index & Jan-08 & Jul-16\\
Venezuela & Dow Jones Venezuela Stock Index & Jan-92 & Jul-07\\
Venezuela & Caracas SE General Index & Jan-94 & Jan-17\\
World & MSCI World Price Index & Jan-76 & Jan-17\\
Zambia & Lusaka SE Index & Jan-02 & Apr-06\\
Zambia & Lusaka SE Index & Jul-11 & Jan-17\\
   \hline
   \hline
\end{tabular*}
\end{threeparttable}
\end{center}
\end{table}

\begin{table}[H]
\caption{Regime changes} \label{tab:regime-changes}
\vspace{-5pt}
\scriptsize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ll}
  \hline
  \hline
  \multicolumn{1}{c}{Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Political Outcome}\\
  \hline
   \multicolumn{3}{c}{\textbf{Coups}}\\ 
\ExpandableInput{../tables/coups.txt} \\
   \multicolumn{3}{c}{\textbf{Failed coup}}\\ 
\ExpandableInput{../tables/failed_coup.txt}\\
  \multicolumn{3}{c}{\textbf{Assassinations}}\\ 
\ExpandableInput{../tables/assassinations.txt}\\
  \multicolumn{3}{c}{\textbf{Resignations}}\\ 
\ExpandableInput{../tables/resignations.txt}
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes: The Polity score is used to classify political outcomes as follows: autocracy = $-10 \leq \rm{score} \leq -6$, anocracy = $-5 \leq \rm{score} \leq 5$, and democracy = $6 \leq \rm{score} \leq 10$.
\end{threeparttable}
\end{center}
\end{table}

\begin{figure}[!ht]
\begin{centering}
\includegraphics[width = 0.6\textwidth]{../figs/daily_mean_absreturn.pdf}
\caption{Absolute value of daily returns}
\label{fig:AV-DR}
\end{centering}
\end{figure}

\begin{figure}[!htb]
\centering
\includegraphics[width = 0.6\textwidth]{../figs/mean-volatility.pdf}
\caption{Mean of volatility estimates from GARCH(1,1) models}
\label{fig:volatility}
\end{figure}

%\clearpage
%\newpage

@@

%\newpage

%\subsection{Volatility} \label{subsec: volatility}

%\newpage

\subsection{Event-level estimates} \label{subsec: coups appendix}

@@

\begin{table}[H]
\caption{Abnormal returns following coups} \label{tab:AR-coups}
\vspace{-5pt}
\scriptsize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
  \hline
  \hline
\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
\cmidrule(r){3-5} \cmidrule(r){6-7}
\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
  \hline
\ExpandableInput{../tables/artable-coups-car.txt}
  \hline
\ExpandableInput{../tables/artable-coups-car-mean.txt}
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes: Standard errors are in parentheses. ``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative). Returns are inflation adjusted. 
\end{threeparttable}
\end{center}
\end{table}

%\subsection{Event-level estimates: assassinations} \label{subsec: ass appendix}

\begin{table}[H]
\caption{Abnormal returns following assassinations} \label{tab:AR-ass}
\vspace{-5pt}
\scriptsize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
  \hline
  \hline
\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
\cmidrule(r){3-5} \cmidrule(r){6-7}
\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
  \hline
\ExpandableInput{../tables/artable-ass-car.txt}
  \hline
\ExpandableInput{../tables/artable-ass-car-mean.txt}
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes: Standard errors are in parentheses. ``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative). Returns are inflation adjusted. 
\end{threeparttable}
\end{center}
\end{table}

%\subsection{Event-level estimates: resignations} \label{subsec: resignation appendix}

\begin{table}[H]
\caption{Abnormal returns following resignations} \label{tab:AR-resignations}
\vspace{-5pt}
\scriptsize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
  \hline
  \hline
\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
\cmidrule(r){3-5} \cmidrule(r){6-7}
\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
  \hline
\ExpandableInput{../tables/artable-res-car.txt}
  \hline
\ExpandableInput{../tables/artable-res-car-mean.txt}
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes: Standard errors are in parentheses. ``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative). Returns are inflation adjusted. 
\end{threeparttable}
\end{center}
\end{table}

%\newpage

@@

%The resignations studied in this paper are those in which leaders left office because of poor performance, public discontent and popular protests. It is therefore not unreasonable to expect the political actions preceding the resignations to have similarly large effects on financial markets. To examine this,

We explore all resignations that were driven by significant popular demonstrations, riots, non-violent civil resistance and other forms of public discontent (see \autoref{tab:protest-list}).\footnote{The set of resignations includes all those listed in either the Coup d'etat Events Handbook or the Archigos Version 4.1 data set with available financial data. In practice, this is the 2011 Egyptian Revolution and the list of resignations in \autoref{tab:AR-resignations}.}

\begin{table}[!htb]
\caption{List of public protests preceding resignations} \label{tab:protest-list}
\vspace{-5pt}
\scriptsize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}llll}
  \hline
    \hline
\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Name}&\multicolumn{1}{c}{Start Date}&\multicolumn{1}{c}{End Date}\\
  \hline
Philippines & EDSA 1/Yellow Revolution & 2/22/1986 & 2/25/1986\\
Bangladesh & Bangladeshi Spring of 1990 & 11/27/1990 & 12/7/1990\\
Thailand & Black May & 5/17/1992 & 5/20/1992\\
Indonesia & Indonesian Riots & 5/12/1998 & 5/21/1998\\
Philippines & EDSA II & 1/17/2001 & 1/20/2001\\
Argentina & Argentina Riots & 12/16/2001 & 12/20/2001\\
Ukraine & Orange Revolution & 11/22/2004 & 1/23/2005\\
Ecuador & Ecuadorian Protests & 4/13/2005 & 4/20/2005\\
Nepal & Nepalese People's Revolution & 4/6/2006 & 4/24/2006\\
Tunisia & Tunisian Revolution & 12/18/2010 & 1/14/2011\\
Egypt & Egyptian Revolution & 1/25/2011 & 2/11/2001\\
   \hline
   \hline
\end{tabular*}
\scriptsize
\end{threeparttable}
\end{center}
\end{table}

%A recent example of a popular uprising preceding a resignation is the 2011 Egyptian Revolution that resulted in the overthrow of President Hosni Mubarak's regime.\footnote{Abnormal returns for this event are not shown in \autoref{tab:AR-resignations} because the stock market was closed on the day of Mubarak's resignation.} Clashes between security forces and protestors led to the deaths of hundreds of citizens and injuries to thousands more. The uprising began on January 25, 2011 when millions of protestors demanded the overthrow of the Egyptian leadership. Examples of public discontent included demonstrations, marches, riots, non-violent civil disobedience, and labor strikes.
%
%The short-term impact of the Egyptian Revolution on the economy was disastrous. As shown in \autoref{fig:CAR-Egypt}, abnormal returns on the Egyptian Stock Exchange Index (EGX 30) were around -7\% on January 26th and -10\% the day after. To prevent further decline during the uprising, the Egyptian Stock Exchange closed at the end of trading on January 27th. President Mubarak resigned on February 11, but the market remained closed until March 23, when CARs declined by another 9\%, before rebounding slightly thereafter.
%
%\begin{figure}[!ht]
%\centering
%\includegraphics[width = 0.6\textwidth]{../figs/egypt-revolution-2011.pdf}
%\caption{Cumulative abnormal returns during the Egyptian revolution}
%\label{fig:CAR-Egypt}
%\end{figure}
%
%An important question is whether other popular uprisings have had similar adverse economic consequences. To examine this, we explore all resignations that were driven by significant public protests.\footnote{The set of resignations includes all those listed in either the Coup d'etat Events Handbook or the Archigos Version 4.1 data set with available financial data. In practice, this is the 2011 Egyptian Revolution and the list or resignations in \autoref{tab:AR-resignations}.} Public protests include popular demonstrations, riots, non-violent civil resistance and other forms of public discontent. We find that both volatility and the absolute value of returns increase during times of protest. Similarly to coups, however, the direction of returns is dependent upon the nature of the protest in question.

@@

Column (1) suggests that public protests have no effect on stock returns. However, this occurs because some political movements increase stock prices while others decrease them. As shown in column (2), the absolute value of stock returns are approximately 1.5\% higher during public protests. These estimates would be biased if protest dates are correlated with higher world or regional stock market indices. To address this potential confounder, column (3) controls for returns on the S\&P/IFC Emerging Markets Investable Composite Stock Index. The coefficient on \textit{Protest} barely changes and the absolute value of returns are still about 1.5\% higher during public protests. Finally, column (4) shows that stock volatility is approximately 1 percentage point higher during political movements.

%\footnote{Volatility estimation methodology is described in detail in \nameref{subsec: Volatility}.}

@@

\begin{table}[!htb]
\caption{Effect of public protests on stock prices} \label{tab:protest-stocks}
\vspace{-5pt}
\scriptsize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}d{1.3}d{1.3}d{1.3}d{1.3}}
  \hline
  \hline
\multicolumn{1}{c}{}&\multicolumn{1}{c}{Returns} & \multicolumn{2}{c}{Absolute Value of Returns}&\multicolumn{1}{c}{Volatility}\\
\cmidrule(r){2-2} \cmidrule(r){3-4} \cmidrule(r){5-5}
 & \multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}\\
  \hline
\ExpandableInput{../tables/protest-regtable.txt}
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes: Standard errors clustered by event are in parentheses.
\end{threeparttable}
\end{center}
\end{table}

%\clearpage
%\pagebreak
%\newpage

%\subsection{Event-level estimates: democratic vs. authoritarian regime changes}

\begin{table}[!htb]
\caption{Abnormal returns following authoritarian regime changes} \label{tab:AR-auth}
\vspace{-5pt}
\scriptsize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
  \hline
  \hline
\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
\cmidrule(r){3-5} \cmidrule(r){6-7}
\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
  \hline
\ExpandableInput{../tables/artable-auth-car.txt}
  \hline
\ExpandableInput{../tables/artable-auth-car-mean.txt}
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes: Standard errors are in parentheses. ``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative). Returns are inflation adjusted. 
\end{threeparttable}
\end{center}
\end{table}
